### 2012-12-28 inst/examples/allee.Rmd
in oscillatory regime with non-negligible noise.  again GP performs nearly optimally while MLE methods suffer greatly

```{r sdp-pars-explore}
sigma_g <- 0.001
sigma_m <- 0.0
z_g = function() rlnorm(1, 0, sigma_g)
z_m = function() 1+(2*runif(1, 0,  1)-1) * sigma_m
x_grid <- seq(0, 1.5 * K, length=101)
h_grid <- x_grid
```

>>>>

```{r sdp-pars-explore}
sigma_g <- 0.05
sigma_m <- 0.0
z_g = function() rlnorm(1, 0, sigma_g)
z_m = function() 1+(2*runif(1, 0,  1)-1) * sigma_m
x_grid <- seq(0, 1.5 * K, length=101)
h_grid <- x_grid
```
